---
title: "Max Allowable Units - San Jose"
output:
  html_document:
    df_print: paged
---
This file takes as an input a parcel file with all the parcels in a location along with zoning information for each parcel.

It outputs the maximum allowable units per parcels given the zoning rules and provided adjustments

Setup
```{r}
library(tidyr)
library(openxlsx)
library(dplyr)
library(janitor)
library(arrow)
library(geojsonio)

rm(list=ls())
options(scipen=999)
```
```{r}
Sys.info()['user']
```

```{r}
### set working directory. if you are running on a different machine than those listed below, add your own machine to the logical tests below
if (Sys.info()["user"]=="ivycao") {
  base_path <- "/Users/ivycao/Library/CloudStorage/GoogleDrive-guangyue.cao@ternerlabs.org/Shared drives/Data Lab -- Terner Housing Innovation Labs/Consulting Projects/Work_AHCS CAYIMBY/SanJose Capacity/"
}

if (Sys.info()["user"]=="Haley") {
  base_path <- "C:/Users/Haley/Documents/terner 2023/"
}

if (Sys.info()["user"]=="haley") {
  base_path <- "C:/Users/haley/OneDrive/Documents/Terner/max units/"
}

if (Sys.info()["user"]=="simon") {
  base_path <- "C:/Users/simon/OneDrive/Documents/Terner/Terner/dashboard/recreation"
  raw <- file.path(base_path, "Dashboard_LA_Pilot/Raw")
  work <- file.path(base_path, "Dashboard_LA_Pilot/Work")
}

```

Inputs
```{r}
## working directory
base_path = base_path

## file with all parcels in the SJ area along with attributes of those parcels
parcel_file = "SanJose_parcel_230601.csv"

## toggles for the simulation you want to test
toggle_sim = "toggle_simulation.xlsx"

## toggles that establish a baseline--these toggles reflect the current policies and should calculate the maximum allowable units in the area if no policy changes take place
toggle_baseline = "toggle_baseline.xlsx"

## hard-coded inputs include all assumptions that apply equally to all parcels
hardcoded_inputs_file = "hardcoded inputs.xlsx"

## a table for the state density bonus
bonus_file = "bmr_bonuses.csv"

## minimum value for max_far_adj for upzone eligible parcels depending on their Gain Sum value
upzone = c(1, 1.25, 1.5)

```

Max Allowable Units Function
```{r}
calc_max_units <- function(base_path
                           ,parcel_file
                           ,toggle_sim
                           ,toggle_baseline
                           ,hardcoded_inputs_file
                           ,bonus_file
                           ,upzone) {
  ### this function takes in baseline toggles and simulation toggles to calculate the maximum allowable units for the parcels provided in the parcel file, using the baseline toggles to calculate parcel characteristics for parcels that are won't be upzoned, and using the simulation toggles to calculate parcel characteristics for parcels that will be upzoned
  
  #### READ IN INPUTS ####
  parcel_base_o <- read.csv(file.path(base_path, parcel_file))
  toggles <- clean_names(read.xlsx(file.path(base_path, toggle_baseline)))
  toggles_sim <- clean_names(read.xlsx(file.path(base_path, toggle_sim)))
  hardcoded_inputs <- clean_names(read.xlsx(file.path(base_path,hardcoded_inputs_file)))
  bonus <- read.csv(file.path(base_path,bonus_file))
  
  parcel_base_o <- parcel_base_o %>% mutate(
    max_du_implied_by_max_dua = ifelse(UNITS_PER_LOT == 99999, 
                                       ifelse(MAX_DUA == 99999, 99999, MAX_DUA * SQFT /43560), UNITS_PER_LOT)
  )
  
  #### TOGGLE ADJUSTMENTS ####
  ### adjust names in toggles file to match
  toggles <- toggles %>%
    mutate(internal_name_merge = gsub("_toggle","", internal_name))
  toggles_sim <- toggles_sim %>%
    mutate(internal_name_merge = gsub("_toggle","", internal_name))
  
  ## convert parcels base ID to character
  parcel_base_o$ID <- as.character(parcel_base_o$ID)
  
  ## define the variable upzone_eligible, which determines if a parcel should be upzoned in the simulation or not
  parcel_base_o <- parcel_base_o %>% mutate(
    upzone_eligible = ifelse((G_CS == 1) | (G_CS == 0 & G_SCS ==1 & max_du_implied_by_max_dua <= 3), 1, 0)
  )
  

  
  ## create max_far_adj, which is the max between several values determined by the upzone vector provided to the function, the max_far_override_val, or the original max far multiplied by the max_far_toggle
  parcel_base <- parcel_base_o %>%
    group_by(ID) %>%
    mutate(
    max_far_adj = case_when(
      upzone_eligible == 0 ~ max(as.numeric(toggles$value[toggles$internal_name == "minmax_far_toggle"])
                                 ,ifelse(toggles$value[toggles$internal_name == "max_far_override_on"] == "on"
                                         , as.numeric(toggles$value[toggles$internal_name == "max_far_override_val"])
                                         , as.numeric(toggles$value[toggles$internal_name == "max_far_toggle"]) * MAX_FAR))
      , GAIN_SUM == 1 ~ max(upzone[1]
                              ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_far_override_on"] == "on"
                                      , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_override_val"])
                                      , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_toggle"]) * MAX_FAR))
      , GAIN_SUM == 2 ~ max(upzone[2]
                              ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_far_override_on"] == "on"
                                      , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_override_val"])
                                      , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_toggle"]) * MAX_FAR))
      , GAIN_SUM == 3 ~ max(upzone[3]
                              ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_far_override_on"] == "on"
                                      , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_override_val"])
                                      , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_toggle"]) * MAX_FAR))
      , TRUE ~ max(as.numeric(toggles_sim$value[toggles_sim$internal_name == "minmax_far_toggle"])
                   ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_far_override_on"] == "on"
                           , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_override_val"])
                           , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_toggle"]) * MAX_FAR))
    )
  )
  
  ## calculate adjusted values for max_du, max_dua, max_height_ft, and max_height_st
  parcel_base <- parcel_base %>%
    group_by(ID) %>%
    mutate(
      
      ## if upzone ineligible, adjust to max_du_override_val if max_du_override is on, adjust to max_du_toggle times units_per_lot times if allow_resid_toggle is off, and adjust to max_du_toggle times 99999 if allow_resid_toggle is on
      ## if upzone eligible, do all the same things but pull the toggles value from toggles_sim, the toggles provided for the simulation
      max_du_adj =  ifelse(upzone_eligible == 0
                          ,ifelse(toggles$value[toggles$internal_name == "max_du_override_on"] == "on"
                               , as.numeric(toggles$value[toggles$internal_name == "max_du_override_val"])
                               ,as.numeric(toggles$value[toggles$internal_name == "max_du_toggle"]) 
                               * ifelse(toggles$value[toggles$internal_name == "allow_resid_toggle"] == "0"
                                        , UNITS_PER_LOT, 99999))
                          ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_du_override_on"] == "on"
                               , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_du_override_val"])
                               ,as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_du_toggle"]) 
                               * ifelse(toggles_sim$value[toggles_sim$internal_name == "allow_resid_toggle"] == "0"
                                        , UNITS_PER_LOT, 99999)))
      
      ## if upzone ineligible, adjust max_dua to the maximum between:
        # the minmax_density toggle value
        # if max_du_override_dua_on is on,
          # the max_du_override_val divided by acres if max_du_override is on, or max_dua_toggle times max_dua if max_du_override is off
          # the max_dua_override_val if max_dua_override is on, or max_dua times the max_dua_toggle
      
      ## if upzone eligible, do all the same things but pull the toggles value from toggles_sim, the toggles provided for the simulation
      ,max_dua_adj = ifelse(upzone_eligible == 0, 
                        max(
                          as.numeric(toggles$value[toggles$internal_name == "minmax_density"])
                          ,ifelse(toggles$value[toggles$internal_name == "max_du_override_dua_on"] == "on"
                                  ,ifelse(toggles$value[toggles$internal_name == "max_du_override_on"] == "on"
                                      ,as.numeric(toggles$value[toggles$internal_name == "max_du_override_val"]) / (SQFT / 43560)
                                      ,as.numeric(toggles$value[toggles$internal_name == "max_dua_toggle"]) * MAX_DUA)
                                  ,ifelse(toggles$value[toggles$internal_name == "max_dua_override_on"] == "on"
                                      ,as.numeric(toggles$value[toggles$internal_name == "max_dua_override_val"])
                                      ,as.numeric(toggles$value[toggles$internal_name == "max_dua_toggle"]) * MAX_DUA)
                          )
                        )
                        ,max(
                          as.numeric(toggles_sim$value[toggles_sim$internal_name == "minmax_density"])
                          ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_du_override_dua_on"] == "on"
                                  ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_du_override_on"] == "on"
                                      ,as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_du_override_val"]) / (SQFT / 43560)
                                      ,as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_dua_toggle"]) * MAX_DUA)
                                  ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_dua_override_on"] == "on"
                                      ,as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_dua_override_val"])
                                      ,as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_dua_toggle"]) * MAX_DUA)
                          )))
      
      ## if upzone ineligible, adjust max_height_ft to be equal to the max of:
        # minmax_height_st_toggle times the feet_per_floor hardcoded input
        # max_height_st_override_val times feet per floor if max_height_st_override is on, and max_height_toggle times building height if max_height_st_override is off
      
      ## if upzone eligible, do all the same things but pull the toggles value from toggles_sim, the toggles provided for the simulation
      ,max_height_ft_adj = ifelse(upzone_eligible == 0, 
                                  max(as.numeric(toggles$value[toggles$internal_name == "minmax_height_st_toggle"]) *
                                        hardcoded_inputs$value[hardcoded_inputs$internal_name == "feet_per_floor"]
                                        , ifelse(toggles$value[toggles$internal_name == "max_height_st_override_on"] == "on"
                                          , as.numeric(toggles$value[toggles$internal_name == "max_height_st_override_val"]) *
                                            hardcoded_inputs$value[hardcoded_inputs$internal_name == "feet_per_floor"]
                                          ,as.numeric(toggles$value[toggles$internal_name =="max_height_toggle"])*BUILDING_HEIGHT), na.rm = TRUE)
                                  ,max(as.numeric(toggles_sim$value[toggles_sim$internal_name == "minmax_height_st_toggle"]) *
                                         hardcoded_inputs$value[hardcoded_inputs$internal_name == "feet_per_floor"]
                                       , ifelse(toggles_sim$value[toggles_sim$internal_name == "max_height_st_override_on"] =="on"
                                                , as.numeric(toggles_sim$value[toggles_sim$internal_name =="max_height_st_override_val"]) *
                                                  hardcoded_inputs$value[hardcoded_inputs$internal_name == "feet_per_floor"]
                                                ,as.numeric(toggles_sim$value[toggles_sim$internal_name =="max_height_toggle"])*BUILDING_HEIGHT), na.rm = TRUE)
      )
      ## if upzone ineligible, adjust max_height_st to be equal to the max of:
        # minmax_height_st_toggle
        # max_height_st_override_val if max_height_st_override is on, and max_height_toggle times HEIGHT_STR if max_height_st_override is off
      
      ## if upzone eligible, do all the same things but pull the toggles value from toggles_sim, the toggles provided for the simulation
      ,max_height_st_adj = ifelse(upzone_eligible == 0,
                                  max(as.numeric(toggles$value[toggles$internal_name == "minmax_height_st_toggle"]),
                                      ifelse(toggles$value[toggles$internal_name == "max_height_st_override_on"] == "on"
                                             , as.numeric(toggles$value[toggles$internal_name == "max_height_st_override_val"])
                                             , as.numeric(toggles$value[toggles$internal_name == "max_height_toggle"]) *
                                               HEIGHT_STR))
                                  ,max(as.numeric(toggles_sim$value[toggles_sim$internal_name == "minmax_height_st_toggle"]),
                                       ifelse(toggles_sim$value[toggles_sim$internal_name == "max_height_st_override_on"] == "on"
                                              , as.numeric(toggles_sim$value[toggles_sim$internal_name =="max_height_st_override_val"])
                                              , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_height_toggle"]) *
                                                HEIGHT_STR)))
      
      ## if upzone ineligible, adjust max_lot_cover to the maximum value between:
        # minmax_lot_cover_toggle
        # max_lot_cover_overrid_val if max_lot_cover_override is on, and the minimum between 1 and max_lot_cover_toggle times lot_cover (if that value is greater than -1)
      
      ## if upzone eligible, do all the same things but pull the toggles value from toggles_sim, the toggles provided for the simulation
      ,max_lot_cover_adj = ifelse(upzone_eligible == 0, 
                                  max(as.numeric(toggles$value[toggles$internal_name == "minmax_lot_cover_toggle"])
                                      , ifelse(toggles$value[toggles$internal_name == "max_lot_cover_override_on"] == "on"
                                               , as.numeric(toggles$value[toggles$internal_name == "max_lot_cover_override_val"])
                                               , min(1 , max(0, as.numeric(toggles$value[toggles$internal_name == "max_lot_cover_toggle"]) + LOT_COVER)))
                                      )
                                  ,max(as.numeric(toggles_sim$value[toggles_sim$internal_name == "minmax_lot_cover_toggle"])
                                       , ifelse(toggles_sim$value[toggles_sim$internal_name == "max_lot_cover_override_on"] == "on"
                                                ,as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_lot_cover_override_val"])
                                                ,min(1,max(0, as.numeric(toggles_sim$value[toggles_sim$internal_name =="max_lot_cover_toggle"]) + LOT_COVER)))))
      
      ## if upzone ineligible, take the minimum value between:
        # max_avg_setback_toggle
        # avg_setback_override_val if avg_setback_override is on, and avg_setback_toggle times SETBK_AVG if avg_setback_override is off
      
      ## if upzone eligible, do all the same things but pull the toggles value from toggles_sim, the toggles provided for the simulation
      ,avg_setback_adj = ifelse(upzone_eligible == 0,
                                min(as.numeric(toggles$value[toggles$internal_name == "max_avg_setback_toggle"])
                                    ,ifelse(toggles$value[toggles$internal_name == "avg_setback_override_on"] == "on"
                                            , as.numeric(toggles$value[toggles$internal_name == "avg_setback_override_val"])
                                            , as.numeric(toggles$value[toggles$internal_name == "avg_setback_toggle"]) * SETBK_AVG)
                                )
                                ,min(as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_avg_setback_toggle"])
                                     ,ifelse(toggles_sim$value[toggles_sim$internal_name == "avg_setback_override_on"] == "on"
                                             , as.numeric(toggles_sim$value[toggles_sim$internal_name =="avg_setback_override_val"])
                                             , as.numeric(toggles_sim$value[toggles_sim$internal_name == "avg_setback_toggle"]) * SETBK_AVG)
                                )
      )
      
      ## if upzone ineligible, adjust min_parking_per_du to be equal to the minimum between:
        #maxmin_parking_per_du_toggle
        # min_parking_override_val if min_parking_override_on is on or min_parking_per_du_toggle times ZN_PARK_MIN
      
      ## if upzone eligible, do all the same things but pull the toggles value from toggles_sim, the toggles provided for the simulation
      ,min_parking_per_du_adj = ifelse(upzone_eligible == 0,
                                       min(as.numeric(toggles$value[toggles$internal_name == "maxmin_parking_per_du_toggle"])
                                           ,ifelse(toggles$value[toggles$internal_name == "min_parking_override_on"] == "on"
                                                   ,as.numeric(toggles$value[toggles$internal_name == "min_parking_override_val"])
                                                   ,as.numeric(toggles$value[toggles$internal_name == "min_parking_per_du_toggle"]) * ZN_PARK_MIN))
                                       ,min(as.numeric(toggles_sim$value[toggles_sim$internal_name == "maxmin_parking_per_du_toggle"])
                                            ,ifelse(toggles_sim$value[toggles_sim$internal_name == "min_parking_override_on"] == "on"
                                                    ,as.numeric(toggles_sim$value[toggles_sim$internal_name == "min_parking_override_val"])
                                                    ,as.numeric(toggles_sim$value[toggles_sim$internal_name =="min_parking_per_du_toggle"]) * ZN_PARK_MIN))
      )
    ) 
    
  ## pull bmr_share value from toggles table
  bmr_share = as.numeric(toggles$value[toggles$internal_name == "bmr_share_toggle"])
  
  ## calculate avg_du_gross_sqft_adj by multiplying avg_du_gross_sqft from the toggles by the hardcoded input, avg_du_gross_sqft
  avg_du_gross_sqft_adj = as.numeric(toggles$value[toggles$internal_name_merge == "avg_du_gross_sqft"]) *
    hardcoded_inputs$value[hardcoded_inputs$internal_name == "avg_du_gross_sqft"]
  
  ## pull the state density bonus from the bmr table, based on bmr_share
  state_dens_bonus <- ifelse(test = bmr_share >= 0.1, bonus$density_bonus_li[bonus$bmr_share == plyr::round_any(bmr_share, .01, f = floor)], 0)
  ## calculate the same values but from the simulation table  
  bmr_share_sim = as.numeric(toggles_sim$value[toggles_sim$internal_name == "bmr_share_toggle"])
  avg_du_gross_sqft_adj_sim = as.numeric(toggles_sim$value[toggles_sim$internal_name_merge == "avg_du_gross_sqft"]) *
    hardcoded_inputs$value[hardcoded_inputs$internal_name == "avg_du_gross_sqft"]
  state_dens_bonus_sim <- ifelse(test = bmr_share_sim >= 0.1, bonus$density_bonus_li[bonus$bmr_share ==plyr::round_any(bmr_share_sim, .01, f = floor)], 0)
  
  ## calculate max_du_final (maximum allowable units) for each parcel
  parcels_env <- parcel_base %>%
    group_by(ID) %>%
    #rowwise() %>%
    mutate(
      ## max_height derived is equal to the minimum between:
        # max_height_st_adj
        # 99999 if max_heigh_ft_adj == 99999, or floor(max_height_ft_adj divided by feet per floor)
      max_height_derived = min(max_height_st_adj, ifelse(max_height_ft_adj==99999, 99999,
                                              floor(max_height_ft_adj/hardcoded_inputs$value[hardcoded_inputs$internal_name == "feet_per_floor"])))
        ## avg_setback_post_bonus is equal to avg_setback_adj (this is where you might add in logic based on TOC or other local bonus programs not present in Fresno)
      ,avg_setback_post_bonus = avg_setback_adj
      ## ADD SJ TOC Here
      ,max_far_post_bonus = ifelse(max_far_adj>=99999
                                   , ifelse(!is.na(servi_tier), toc_max_far, max_far_adj)
                                   , max(max_far_adj, ifelse(!is.na(servi_tier), toc_max_far, max_far_adj)))
      ,max_height_post_bonus = max_height_derived
      
      ## max_dua_post_state_bonus is equal to max_dua_adj * (1 + state density bonus), where the value of the state density bonus is different if the parcel is upzone eligible or not
      ,max_dua_post_state_bonus = ifelse(upzone_eligible == 0, 
                                          max_dua_adj * (1 + state_dens_bonus)
                                          ,max_dua_adj * (1 + state_dens_bonus_sim))
      
      ## again, in this case we could remove max_dua_post_TOC_bonus altogether since it is simply always equal to max_dua_adj, but it is left here in case you want to add logic for local bonus programs
      ## ADD SJ TOC Here
      ,max_dua_post_TOC_bonus = ifelse(max_dua_adj >=99999
                                       , ifelse((!is.na(servi_tier)) & (RESI_ALLOWED == 1), toc_max_dua, max_dua_adj)
                                       , max(max_dua_adj, ifelse((!is.na(servi_tier)) & (RESI_ALLOWED == 1), toc_max_dua, max_dua_adj)))
      ,max_dua_post_bonus = ifelse(max_dua_post_state_bonus >=99999
                                   , max_dua_post_TOC_bonus
                                   , max(max_dua_post_TOC_bonus, max_dua_post_state_bonus))
      ## ADD SJ TOC Here
      ,min_parking_per_du_post_bonus = min(min_parking_per_du_adj, ifelse(!is.na(servi_tier), toc_max_parking, min_parking_per_du_adj))
      
      ## max_lot_cover_derived is equal to the minimum between:
        # max_lot_cover_adj
        # rad(lot size) - 2 * avg_setback_adj, or 0 if this value is negative, squared and divided by lot size
      ,max_lot_cover_derived = min(max_lot_cover_adj, max(0,(SQFT ^ (1/2) - 2 * avg_setback_adj)) ^2 / SQFT)
      
      ## max_sqft_alt1 is equal to lot size times max_far_post_bonus
      ,max_sqft_alt1 = SQFT * max_far_post_bonus
      
      ## max_sft_alt2  is equal to lot size times max_lot_cover_derived times max_height_post_bonus
      ,max_sqft_alt2 = SQFT * max_lot_cover_derived * max_height_post_bonus
      
      ## max_sqft_derived_post_bonus is equal to the minimum between max sqft alternative 1 and max sqft alternative 2
      ,max_sqft_derived_post_bonus = min(max_sqft_alt1, max_sqft_alt2)
      ,max_du_alt1 = max_du_adj
      
      ## max_du_alt2 is equal to max_dua_post_bonus times lot size converted to acres
      ,max_du_alt2 = max_dua_post_bonus * SQFT * .0000229568
      
      ## max_du_alt3 is equal to max_sqft_derived_post_bonus divided by avg_du_gross_sqft_adj, where the value of avg_du_gross_sqft_adj depends on if the parcel is upzone eligible or not 
      ,max_du_alt3 = ifelse(upzone_eligible == 0,
                             max_sqft_derived_post_bonus / avg_du_gross_sqft_adj
                             ,max_sqft_derived_post_bonus / avg_du_gross_sqft_adj_sim)
      ## max_du_final is equal to the ceiling of the minimum between max du alternatives 1, 2, and 3
      ,max_du_final = ceiling(min(max_du_alt1, max_du_alt2, max_du_alt3))
      
      ## max_tech_feasible_du is technically not needed to calculate max allowable units, but I included it anyway since it's in the pro forma
      ,max_tech_feasible_du = floor(hardcoded_inputs$value[hardcoded_inputs$internal_name == "max_density_hi_rise"] * (SQFT / 43560))
    )
  
  ## In San Jose, the zones below are non-residential
  ## adjust the max_du_final for all non-residential zones to be equal to 0
  parcels_env$max_du_final[parcels_env$BASE_ZONING %in% c('HI', 'A', 'IP', 'LI', 'CO', 'CIC', 'PQP', 'OS', 'R-MH', 'TEC',
       'MS-G', 'MS-C', 'CN', 'UVC',"<Null>")] <- 0
  
  ## return all of the parcels withe max_du_final calculated
  return(parcels_env)
}

```


To run the function, provide the parcel information, toggles, hardcoded inputs, bmr table, and upzone values.
We are going to apply the function to all parcels in Fresno under two scenarios:
  1) sim_output - under this scenario, all upzone eligible parcels will have new toggles provided in the toggle_simulation.xlsx file. The upzone eligible parcels will then have new maximum allowable units numbers based on adjusted parcel characteristics like max_far, max_du, etc.
  
  2) baseline_output - under this scenario, all parcels (both upzone eligible and upzone ineligible) will use the same toggles in order to run a scenario where no upzoning takes place. In order to do this, toggle_baseline is provided as the toggle file for bother the toggle_sim input and the toggle_baseline input. The upzone vector is also adjusted to c(-999, -999, -999) so that the values in the upzone vector are never chosen as the value for max_far_adj


```{r}
parcel_file = "parcel_sample.csv"
toggle_sim = "toggle_simulation.xlsx"
toggle_baseline = "toggle_baseline.xlsx"
hardcoded_inputs_file = "hardcoded inputs.xlsx"
bonus_file = "bmr_bonuses.csv"
upzone = c(1, 1.25, 1.5)

test_parcel <- read.csv(file.path(base_path, parcel_file))
toggles <- clean_names(read.xlsx(file.path(base_path, toggle_baseline)))
toggles_sim <- clean_names(read.xlsx(file.path(base_path, toggle_sim)))
hardcoded_inputs <- clean_names(read.xlsx(file.path(base_path,hardcoded_inputs_file)))
bonus <- read.csv(file.path(base_path,bonus_file))
  
test_parcel <- test_parcel %>% mutate(
  max_du_implied_by_max_dua = ifelse(UNITS_PER_LOT == 999999999, 
                                    ifelse(MAX_DUA == -1, -1, MAX_DUA * SQFT /43560), UNITS_PER_LOT)
)

 #### TOGGLE ADJUSTMENTS ####
  ### adjust names in toggles file to match
  toggles <- toggles %>%
    mutate(internal_name_merge = gsub("_toggle","", internal_name))
  toggles_sim <- toggles_sim %>%
    mutate(internal_name_merge = gsub("_toggle","", internal_name))
  
  ## convert parcels base ID to character
  test_parcel$ID <- as.character(test_parcel$ID)
  
  ## define the variable upzone_eligible, which determines if a parcel should be upzoned in the simulation or not
  test_parcel <- test_parcel %>% mutate(
    upzone_eligible = ifelse((G_CS == 1) | (G_CS == 0 & G_SCS ==1 & max_du_implied_by_max_dua <= 3), 1, 0)
  )
  
  ## create max_far_adj, which is the max between several values determined by the upzone vector provided to the function, the max_far_override_val, or the original max far multiplied by the max_far_toggle
  test_parcel <- test_parcel %>% 
    group_by(ID) %>%
    mutate(
    max_far_adj = case_when(
      TRUE ~ max(as.numeric(toggles_sim$value[toggles_sim$internal_name == "minmax_far_toggle"])
                   ,ifelse(toggles_sim$value[toggles_sim$internal_name == "max_far_override_on"] == "on"
                           , as.numeric(toggles_sim$value[toggles_sim$internal_name == "max_far_override_val"])
                           , MAX_FAR)))
    ,test_col = ifelse(!is.na(servi_tier), toc_max_parking, ZN_PARK_MIN)
  )
  test_parcel
```
```{r}
min(2, 3, NA, na.rm = TRUE)
```


```{r}
sim_output <- calc_max_units(base_path = base_path
                             , parcel_file = "SanJose_parcel_230601.csv"
                             , toggle_sim = "toggle_simulation.xlsx"
                             , toggle_baseline = "toggle_baseline.xlsx"
                             , hardcoded_inputs_file = "hardcoded inputs.xlsx"
                             , bonus_file = "bmr_bonuses.csv"
                             , upzone = c(1, 1.25, 1.5))

baseline_output <- calc_max_units(base_path = base_path
                                  , parcel_file = "SanJose_parcel_230601.csv"
                                  , toggle_sim = "toggle_baseline.xlsx"
                                  , toggle_baseline = "toggle_baseline.xlsx"
                                  , hardcoded_inputs_file = "hardcoded inputs.xlsx"
                                  , bonus_file = "bmr_bonuses.csv"
                                  , upzone = c(-999, -999, -999))

### here we calculate the total maximum allowable units under each scenario
sum(sim_output$max_du_final,na.rm=T)
sum(baseline_output$max_du_final,na.rm=T)

```

```{r}
nrow(sim_output)
nrow(baseline_output)
```
```{r}
sum(sim_output$UNITS_PER_LOT,na.rm=T)
#sum(baseline_output$ACRES,na.rm=T)
```

This code will combine all variables from the simulation output with the max_du_final variable from the baseline output and write the combined table to a csv for QC purposes
```{r}

output_comb <- sim_output %>% left_join(baseline_output %>% mutate(baseline_max_du = max_du_final) %>% select(ID, baseline_max_du), by = "ID")
output_comb %>% write.csv("max_du_combined_output.csv")


```